On Extensibility and Personalizability of Multi-Modal Trip Planning

### 2016-03-02 paper.tex
Added figures. Need to change Figure 3 though.

\newcommand{\aux}{\mathit{aux}}
\newcommand{\dist}{\mathit{dist}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\tit}[1]{\textit{#1}}
\newcommand{\IFF}{\textit{iff}}
\newcommand{\IF}{\textit{if}}
\newcommand{\PCF}{\mathit{PCF}}
\newcommand{\walk}{\mathit{walk}}
\newcommand{\bike}{\mathit{bike}}
\newcommand{\car}{\mathit{car}}
\newcommand{\public}{\mathit{public}}
\newcommand{\taxi}{\mathit{taxi}}
\newcommand{\gas}{\mathit{gas}}
\newcommand{\wait}{\mathit{wait}}
\newcommand{\SUM}{\mathit{sum}}
\newcommand{\MAX}{\mathit{max}}
\newcommand{\MIN}{\mathit{min}}
\newcommand{\AVG}{\mathit{avg}}

@@

Formally, let $A$ be the auxiliary set of lat-long pairs, 
$N$ a node in our planner and $r$ the effective radius.
We first compute the set $P$ of auxiliary points such that
$P \subseteq A$ and $\dist(p,N)<r$ for all $p \in P$.
Then, the total score of auxiliary data for $N$ with respect to $P$ and $r$,
denoted by $S_\aux(N,P,r)$, is computed as follows.

\begin{equation}
	S_\aux(N,P,r) = \sum_{\substack{p \in P}} \Big(1 - \frac{\dist(p,N)}{r}\Big)
\end{equation}

@@

An intuitive constraint in trip planning could be ``I will never drive after biking or
taking the public transit."
In LTL, such constraint can be translated into an LTL formula
\begin{align*}
	\psi = ((M=b) \lor (M=p)) \,\cA\, (\Box (\neg (M=c))).
\end{align*}

@@

\subsection{Reasoning with Constraints and Preferences}
\begin{itemize}
	\setlength\itemsep{1pt}
	\item Describe why and how we integrate constraints and preferences into A*.
\end{itemize}

We leveraged the widely-used A* search algorithm on top of our high-performance graph search
engine.  The A* algorithm incorporates the following cost function.
\begin{equation}
	f(S) = g(S) + h(S),
\end{equation}
where $g(S)$ is the cost of an optimal trip from the initial state to $S$, and
$h(S)$ is an admissible estimate of the cost of an optimal trip from $S$ to goal.

@@

%\section{User Study}
%\begin{itemize}
%	\setlength\itemsep{1pt}
%	\item Describe the set up of our experiments on AMT and explain why: because we want to evaluate the
%				feasibility of the three features.
%	\item Describe the results.
%\end{itemize}
\section{Implementation}

\begin{itemize}
	\setlength\itemsep{1pt}
	\item Describe the system structure.
	\item Describe the input to the system.
	\item Describe the output from the system.
\end{itemize}

>>>>

\newcommand{\aux}{\mathit{aux}}
\newcommand{\dist}{\mathit{dist}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cU}{\mathcal{U}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\tit}[1]{\textit{#1}}
\newcommand{\IFF}{\textit{iff}}
\newcommand{\IF}{\textit{if}}
\newcommand{\PCF}{\mathit{PCF}}
\newcommand{\walk}{\mathit{walk}}
\newcommand{\bike}{\mathit{bike}}
\newcommand{\car}{\mathit{car}}
\newcommand{\public}{\mathit{public}}
\newcommand{\taxi}{\mathit{taxi}}
\newcommand{\gas}{\mathit{gas}}
\newcommand{\wait}{\mathit{wait}}
\newcommand{\SUM}{\mathit{sum}}
\newcommand{\MAX}{\mathit{max}}
\newcommand{\MIN}{\mathit{min}}
\newcommand{\AVG}{\mathit{avg}}

@@

Formally, let $\cU$ be the uploaded auxiliary dataset of lat-long pairs, 
$N=(x_N,y_N)$ a node in our planner and $r$ the effective radius.
We first compute the set $\cP \subseteq A$ of auxiliary points such that,
for every node $P \in \cP$, the Euclidean distance between $N$ and $P$
is within $r$.
Then, the score of auxiliary data for $N$ with respect to $\cP$ and $r$,
denoted by $S(N,\cP,r)$, is computed as follows.

\begin{equation*}
	S(N,\cP,r) = \sum_{\substack{P \in \cP}} 
		\Big(1 - \frac{\sqrt{(x_N-x_P)^2+(y_N-y_P)^2}}{r}\Big)
\end{equation*}

Now we turn to \figref{aux} for an instance to show how auxiliary data
are integrated into the graph using the equation above.
In \figref{aux}, we have the green nodes denoting the graph nodes, 
and the red nodes the new auxiliary nodes that represent locations
of criminal events.
For node $N$, there are three red nodes within its neighborhood of
radius of $r$; thus, we have $\cP=\{P_1,P_2,P_3\}$.
We assume $r$ is 100 feet, and the distances from $N$ to $P_1$,
$P_2$ and $P_3$ are 25, 80 and 90 feet, respectively.
Then, the crime score of $S(N,\cP,r)$ is $1.05$.

\begin{figure}[!ht]
  \centering
    \includegraphics[width=0.4\textwidth]{figs/aux.pdf}
  \caption{Integrating uploaded data\label{fig:aux}}
\end{figure}

@@

A natural constraint in trip planning could be ``In this trip I will not drive a car 
after biking or taking the public transit."
In LTL, such constraint can be translated into an LTL formula
\begin{align*}
	\psi = ((M=b) \lor (M=p)) \,\cA\, (\Box (\neg (M=c))).
\end{align*}

@@

\subsection{Reasoning with Constraints and Preferences}
%\begin{itemize}
%	\setlength\itemsep{1pt}
%	\item Describe why and how we integrate constraints and preferences into A*.
%\end{itemize}

\begin{figure}[!ht]
  \centering
    \includegraphics[width=0.4\textwidth]{figs/Astar.pdf}
  \caption{Adjusted A*\label{fig:astar}}
\end{figure}

We leveraged the widely-used A* search algorithm on top of our high-performance graph search
engine (cf. \figref{astar}).  The A* algorithm incorporates the following cost function.
\begin{equation}
	f(S) = g(S) + h(S),
\end{equation}
where $g(S)$ is the cost of an optimal trip from the initial state to $S$, and
$h(S)$ is an admissible estimate of the cost of an optimal trip from $S$ to goal.

@@

%\section{User Study}
%\begin{itemize}
%	\setlength\itemsep{1pt}
%	\item Describe the set up of our experiments on AMT and explain why: because we want to evaluate the
%				feasibility of the three features.
%	\item Describe the results.
%\end{itemize}
\section{Implementation and Results}
%\begin{itemize}
%	\setlength\itemsep{1pt}
%	\item Describe the system structure.
%	\item Describe the input to the system.
%	\item Describe the output from the system.
%\end{itemize}

\subsection{System Architecture}
\begin{figure*}[!ht]
  \centering
    \includegraphics[width=0.8\textwidth]{figs/system.pdf}
  \caption{System Overview\label{fig:system}}
\end{figure*}

\subsection{Results}
First, we show resulting route for Alice in \figref{alice}.
\begin{figure}[!ht]
  \centering
    \includegraphics[width=0.5\textwidth]{figs/result_Alice.pdf}
  \caption{Resulting route for Alice\label{fig:alice}}
\end{figure}

Second, we show resulting route for Bob in \figref{bob}.
\begin{figure}[!ht]
  \centering
    \includegraphics[width=0.5\textwidth]{figs/result_Bob.pdf}
  \caption{Resulting route for Bob\label{fig:bob}}
\end{figure}

Third, we show resulting route for Cal in \figref{cal}.
\begin{figure}[!ht]
  \centering
    \includegraphics[width=0.5\textwidth]{figs/result_Cal.pdf}
  \caption{Resulting route for Cal\label{fig:cal}}
\end{figure}
